Architectures for workflow integration in science gateways

### 2016-04-15 paper.tex
Updates in section 3.5

\subsection{Pool model}
\label{sec:pool}
See Figure~\ref{archi:agent}. Workflows are submitted by the science
gateway to a pool to which agents connect asynchronously to retrieve
and execute workflows (interaction \texttt{f}). Agents may be started
according to various policies, for instance to ensure load
balancing. Agents may wrap different types of workflow engines. This
model was implemented in the SHIWA pool~\cite{ROGE-13}.

>>>>

\subsection{Pool model}
\label{sec:pool}
See Figure~\ref{archi:agent}. Workflows are submitted by the science
gateway to a pool through interaction \texttt{d}. Agents connect to
the pool asynchronously to retrieve and execute workflows through
interaction \texttt{f}. Agents may be started according to various
policies, for instance to ensure load balancing. Agents may wrap
different types of workflow engines. Workflow engine controls tasks
and data on the infrastructure through interactions \texttt{b} and
\texttt{c$_2$}, science gateway transfers user data through
interaction \texttt{c$_1$}, and administrator installs workflow
dependencies through interaction \texttt{a$_1$}.

The pool model was implemented in the SHIWA pool~\cite{ROGE-13}, see
Figure~\ref{fig:shiwa-pool-architecture}. In Figure
~\ref{fig:shiwa-pool-architecture}, interaction \texttt{d} of
Figure~\ref{archi:agent} is implemented in 3 different types of calls
to the pool: workflow submission (\texttt{1} \& \texttt{2}), workflow
status retrieval (\texttt{a} and \texttt{b}), and workflow retrieval
(\texttt{13} \& \texttt{14}). In Figure
~\ref{fig:shiwa-pool-architecture}, interaction \texttt{f} of
Figure~\ref{archi:agent} is implemented through 2 types of calls:
workflow instance retrieval (\texttt{4}, \texttt{5} and \texttt{6}),
and workflow instance update (\texttt{11} and \texttt{12}). Workflow
instance retrieval is used by the agents to fetch work from the
pool. Workflow instance update is used by the agents to update
workflow statuses. In the SHIWA pool, agents can wrap different types
of workflow engines to execute workflows expressed with different
languages. Calls \texttt{0}, \texttt{7}, \texttt{8} and \texttt{9} are
used by workflow engine plugins to declare their supported language
and launch engines, and by workflow engines to report their status to
the agent. These calls are specific to the SHIWA Pool implementation
of the \texttt{agent} component and therefore have no corresponding
representation in Figure~\ref{archi:agent}.

\begin{figure*}
\centering
\includegraphics[width=1.5\columnwidth]{figures/pool-interactions.pdf}
\caption{Architecture of the SHIWA pool (Figure reproduced
  from~\cite{ROGE-13}). Circle-terminated arrows indicate messages
  that are broadcast to all pool clients.}
\label{fig:shiwa-pool-architecture}
\end{figure*}
